Report

### 2020-10-12 report.Rmd
Add piscivory statistics

---
title: "Report"
author: "Alain Danet"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
---

@@

library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
library(viridis)
source("R/misc.R") # Define your custom code as a bunch of functions.
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

@@

# Statistical models

## Raw bm

```{r, eval = TRUE}
loadd(model_bm, model_bm_vif)

model_bm_vif %>%
  ggplot(aes(y = vif, x = term)) +
  geom_hline(yintercept = 10) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(model_type~variable, scales = "free")
```

```{r, eval = FALSE}
library(yhat)
test <- model_int$mod3[[1]]
CCData <- commonalityCoefficients(model_int$data[[1]],
  "linear_slope",
  list("bm_slope", "inc_f", "bm"), "F")
CCData

test_data <- model_int$data[[1]]
lm_test <- lm(
  formula = linear_slope ~ bm_slope*inc_f*bm,
  weights = reg_weight
)
test <- regr(lm_test)
```

### Effect of protocol type on the model validity

```{r}
loadd(model_bm_by_protocol, model_bm_by_protocol_vif)

protocol_vec <- model_bm_by_protocol_vif$protocol_type %>% unique
p_vif_protocol <- map(protocol_vec, function (x) {
  model_bm_by_protocol_vif %>%
    filter(protocol_type == x) %>%
    ggplot(aes(y= vif, x = term)) +
    geom_hline(yintercept = 10) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = paste0("Protocol type: ", x)) +
    facet_grid(model_type~variable, scales = "free_y")
  })
p_vif_protocol[[1]]
p_vif_protocol[[2]]
```

```{r, eval = FALSE}
filter(model_bm_by_protocol_vif, model_type == "mod_bm_quad")
```

```{r}
loadd(bm_net_group)
bm_net_group %>%
  filter(variable == "connectance") %>%
  ggplot(aes(x = bm_slope, y = bm)) +
  geom_point()
```

### Current best model

$$
Y = \alpha + \beta_1D_b + \beta_2D_bI_b + \beta_3D_bI_bB
$$

```{r, eval = TRUE}
loadd(model_bm_by_protocol_summary)
model_bm_by_protocol_summary %<>%
  filter(protocol_type == "complete")
```

```{r, eval = FALSE}
filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["anova"]]

filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["anova"]]

filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["anova"]]

filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["anova"]]
```

```{r, eval = TRUE}
pred <- model_bm_by_protocol_summary %>%
  filter(model == "mod_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

```{r}
pred <- model_bm_by_protocol_summary %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
plot_grid(plotlist = pred$plot_data, labels = pred$variable)
```

```{r}
loadd(model_bm_summary)
```

```{r, eval = FALSE}
filter(model_bm_summary, model == "mod_inc_bm")[["resume"]]
filter(model_bm_summary, model == "mod_inc_bm")[["anova"]]

filter(model_bm_summary, model == "mod_bm_inc")[["resume"]]
filter(model_bm_summary, model == "mod_bm_inc")[["anova"]]

filter(model_bm_summary, model == "mod_bm_quad")[["resume"]]
filter(model_bm_summary, model == "mod_bm_quad")[["anova"]]

filter(model_bm_summary, model == "mod_bm_quad2")[["resume"]]
filter(model_bm_summary, model == "mod_bm_quad2")[["anova"]]
```

```{r}
pred_bm_quad2 <- model_bm_summary %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
plot_grid(plotlist = pred_bm_quad2$plot, labels = pred_bm_quad2$variable)
pred_bm_quad2_plot <- map2(model_bm$data, pred_bm_quad2$pred_df, plot_pred_data)

plot_grid(plotlist = pred_bm_quad2_plot, labels = pred_bm_quad2$variable)

pred_bm_quad <- model_bm_summary %>%
  filter(model == "mod_bm_quad") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

pred_bm_quad_plot <- map2(model_bm$data, pred_bm_quad$pred_df, plot_pred_data)
plot_grid(plotlist = pred_bm_quad_plot, labels = pred_bm_quad2$variable)
```

```{r}
#model_bm$data[[1]] %>%
  #ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
  #scale_fill_viridis() +
  #geom_point() +
  #geom_line(
    #data = pred_bm_quad2$pred_df[[1]] %>%
      #rename(bm_f = group, bm_slope = x, linear_slope = predicted),
    #aes(y = linear_slope, x = bm_slope, color = bm_f),
    #inherit.aes = FALSE)

test <- map2(model_bm$data, pred_bm_quad2$pred_df, function (.data, pred) {

  .data %>%
    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
    scale_fill_viridis() +
    geom_point() +
    geom_line(
      data = pred %>%
	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
      aes(y = linear_slope, x = bm_slope, color = bm_f),
      inherit.aes = FALSE)

    })
plot_grid(plotlist = test)
```

```{r}
test <- map2(model_bm$data, pred_bm_quad$pred_df, function (.data, pred) {

  .data %>%
    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
    scale_fill_viridis() +
    geom_point() +
    geom_line(
      data = pred %>%
	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
      aes(y = linear_slope, x = bm_slope, color = bm_f),
      inherit.aes = FALSE)

    })
plot_grid(plotlist = test, labels = model_bm$variable)
```

### Is the model valid with log_bm ?

@@

```{r}
log_bm_net_group %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
  geom_point() +
  scale_color_viridis() +
  #geom_smooth(method = "lm") +
  facet_grid(variable~protocol_type, scales = "free") +
  labs(title = "Log biomass")

log_bm_net_group %>%
  filter(variable == "connectance") %>%
  ggplot(aes(x = bm_slope, y = bm)) +
  geom_point()
```

@@

```{r, eval = FALSE}
filter(model_log_bm_summary, model == "mod_inc_bm")[["resume"]]
filter(model_log_bm_summary, model == "mod_inc_bm")[["anova"]]

filter(model_log_bm_summary, model == "mod_bm_inc")[["resume"]]
filter(model_log_bm_summary, model == "mod_bm_inc")[["anova"]]

filter(model_log_bm_summary, model == "mod_bm_quad")[["resume"]]
filter(model_log_bm_summary, model == "mod_bm_quad")[["resume"]] %>%
  map(., ~ .x$r.squared)
filter(model_log_bm_summary, model == "mod_bm_quad")[["anova"]]

filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]]
filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]] %>%
  map_dbl(., ~ .x$r.squared)

filter(model_log_bm_summary, model == "mod_bm_quad2")[["anova"]]
filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]]

filter(model_log_bm_summary, model == "mod_log_bm_quad2")[["anova"]]
filter(model_log_bm_summary, model == "mod_log_bm_quad2")[["resume"]] %>%
  map_dbl(., ~ .x$r.squared)
```

@@

```{r}
pred_log_bm_quad2 <- model_log_bm_summary %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

@@

```{r, eval = FALSE}
filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["resume"]]
filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["anova"]]
```

```{r}
pred <- model_log_bm_by_protocol_summary %>%
  filter(model == "mod_log_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

@@

## Biomass classification

```{r}
loadd(rigal_classification)
myload(biomass_ts_sax, envir = globalenv(),dir = get_mypath("data"))

biomass_classif_rigal <- rigal_classification %>%
  filter(variable %in% c("bm_std", "log_bm_std")) %>%
  unnest(classif) %>%
  mutate(station = as.character(station)) %>%
  select(station, variable,shape_class)

p_biomass_classif_rigal <- biomass_classif_rigal %>%
  ggplot(aes(x = shape_class)) +
  geom_bar() +
  facet_wrap(~variable) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Temporal dynamics

```{r}
p_cap <- paste0(
  "Temporal dynamics of biomass and temporal dynamics of
  metrics for 10 randomly selected communities."
)
```

```{r p-tmp-dyn, cache = TRUE, eval = FALSE}

p <- vector(mode = "list", length = 10)
for (i in seq_len(length(p))) {
  to_plot <- temporal_dynamics_plot %>% 
    filter(station == sample(temporal_dynamics_plot$station, 1))
  p[[i]] <- cowplot::plot_grid(plotlist = to_plot$plot, labels = to_plot$station)
}
p
```

## Temporal dynamics decrease/increase constant

### Log biomass

```{r, cache = TRUE, fig.height = 45}
st_decrease_increase_rigal <- biomass_classif_rigal %>%
  filter(variable == "log_bm_std") %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))
data_decrease_increase <- full_data2 %>%
  filter(station %in% st_decrease_increase_rigal$station)

log_bm_min_max <- map_dbl(c(min, max),
  ~.x(data_decrease_increase$log_bm_std, na.rm = TRUE))
nb_year_min_max <- map_dbl(c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot$plot %<>%
  map(., ~ .x + lims(y = log_bm_min_max, x = nb_year_min_max))

temporal_dynamics_plot %>%
  filter(variable == "log_bm_std", station %in% st_decrease_increase_rigal$station) %>%
  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
```

### Raw Biomass

```{r, cache = TRUE, fig.height = 45}
st_decrease_increase_rigal_biomass <- rigal_classification %>%
  filter(variable == "bm_std") %>%
  unnest(classif) %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))

bm_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$bm_std, na.rm = TRUE))
nb_year_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot[temporal_dynamics_plot$variable == "bm_std",]$plot %<>%
  map(., ~ .x + lims(y = bm_min_max, x = nb_year_min_max))

temporal_dynamics_plot %>%
  filter(variable == "bm_std", station %in% st_decrease_increase_rigal_biomass$station) %>%
  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal_biomass$station)
```

### Richness

```{r, cache = TRUE, fig.height = 45}
var_tmp <- "rich_std"
st_decrease_increase_rigal <- rigal_classification %>%
  filter(variable == var_tmp) %>%
  unnest(classif) %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))

min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase[[var_tmp]], na.rm = TRUE))
nb_year_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot[temporal_dynamics_plot$variable == var_tmp,]$plot %<>%
  map(., ~ .x + lims(y = min_max, x = nb_year_min_max))

temporal_dynamics_plot %>%
  filter(variable == var_tmp, station %in% st_decrease_increase_rigal$station) %>%
  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
```

### Number of nodes

```{r, cache = TRUE, fig.height = 45}
var_tmp <- "nbnode_std"
st_decrease_increase_rigal <- rigal_classification %>%
  filter(variable == var_tmp) %>%
  unnest(classif) %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))

min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase[[var_tmp]], na.rm = TRUE))
nb_year_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot[temporal_dynamics_plot$variable == var_tmp,]$plot %<>%
  map(., ~ .x + lims(y = min_max, x = nb_year_min_max))

temporal_dynamics_plot %>%
  filter(variable == var_tmp, station %in% st_decrease_increase_rigal$station) %>%
  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
```

@@

p_rigal_decrease_increase_slope_st <- 
  st_decrease_increase_rigal_biomass %>%
  left_join(biomass_group, by = "station") %>%
  ggplot(aes(y = linear_slope, x = bm_slope, color = shape_class)) +
  geom_point() +
  facet_wrap(~variable)
p_rigal_decrease_increase_slope_st
```

### Tendancies in rigal increase / decrease

@@

>>>>

---
title: "Report"
author: "Alain Danet"
date: "`r Sys.Date()`"
tables: yes
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
---

@@

library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
library(viridis)
library(kableExtra)
source("R/misc.R") # Define your custom code as a bunch of functions.
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

@@

- Methodological choice:
  - Dynamics of log of the biomass: put big and little station on the same scale
    (% of biomass gained or lost per year)

@@

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_wrap(~variable, scales = "free") +
  labs_log_bm_net_trends()
```

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_grid(variable~protocol_type, scales = "free") +
  labs_log_bm_net_trends()

log_bm_net_group %>%
  filter(variable == "connectance") %>%
  ggplot(aes(x = bm_slope, y = bm)) +
  geom_point()
  labs(x = "Biomass trends (log biomass per year)", y = "Biomass")
```

@@

```{r, eval = TRUE}
#https://stackoverflow.com/questions/44457243/regression-tables-in-r-markdown-rmarkdown-html-pdf

unique(model_log_bm_summary$variable)
model_log_bm_table <- model_log_bm_summary %>%
  filter(model == "mod_bm_quad2") %>%
  filter(!variable %in% c("log_rich_std", "nbnode_std")) %>%
  mutate(
    reg_table = map(model_obj, broom::tidy),
    anova_table = map(anova, broom::tidy)
  )

model_log_bm_table[["reg_table"]] %>% 
  bind_rows(.) %>%
  mutate(variable = rep(model_log_bm_table[["variable"]], each = 6)) %>%
  select(variable, everything()) %>%
  kable(.,
    booktabs = TRUE, 
    caption = 
      paste0(
      "Regression table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    ) 
  )
```

```{r}
bind_rows(model_log_bm_table[["anova_table"]]) %>% 
  mutate(variable = rep(model_log_bm_table[["variable"]], each = 6)) %>%
  select(variable, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  )

```{r}
map_dfr(model_log_bm_table[["model_obj"]], broom::glance) %>%
  mutate(variable = model_log_bm_table[["variable"]]) %>%
  select(variable, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Model summary for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  )
```

@@

```{r, fig.height = 12, fig.width = 12}
pred_log_bm_quad2 <- model_log_bm_summary %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

@@

@@

@@

p_rigal_decrease_increase_slope_st <- 
  st_decrease_increase_rigal_biomass %>%
  left_join(biomass_group, by = "station") %>%
  ggplot(aes(y = linear_slope, x = bm_slope, color = shape_class)) +
  geom_point() +
  facet_wrap(~variable)
p_rigal_decrease_increase_slope_st
```
### Tendancies in rigal increase / decrease

@@

## Other Statistical model

```{r, eval = FALSE}
complete_log_quad2 <- model_log_bm_by_protocol_summary %>%
  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
  mutate(
    reg_table = map(model_obj, broom::tidy),
    anova_table = map(anova, broom::tidy)
  )

complete_log_quad2[["reg_table"]] %>% 
  bind_rows(.) %>%
  mutate(variable = rep(complete_log_quad2[["variable"]], each = 6)) %>%
  select(variable, everything()) %>%
  kable(.,
    booktabs = TRUE, 
    caption = 
      paste0(
      "Regression table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    ) 
  )

complete_log_quad2[["anova_table"]] %>% 
  bind_rows(.) %>%
  mutate(variable = rep(complete_log_quad2[["variable"]], each = 6)) %>%
  select(variable, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  )
```
